Bayesian statistics and swine flu

### 2009-08-12 docs/pandemic/bayesPandemic.rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@358 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\documentclass{beamer}
\usepackage[nogin]{Sweave}
\title{Bayesian statistics and  swine flu}
\author{Patrick Brown$^1$,  Peter Neal$^2$}
\institute{1:Cancer Care Ontario and Dalla Lana School of Public Health, University of Toronto; 2: School of Mathematics, University of Manchester} 
\usepackage{amsmath,subfigure,alltt}

@@

\begin{block}{Histogram}
<<histPost>>=
hist(paramSample[,"probs.D"], breaks=12)
abline(v=params$probs["D"], col="red")
@
\end{block}
\end{columns}
\end{frame}
\end{document}

>>>>

\documentclass{beamer}
\usepackage[nogin]{Sweave}
\title{Bayesian statistics and  swine flu}
\author{Patrick Brown$^1$,  Peter Neal$^2$}
\institute{1:Cancer Care Ontario and Dalla Lana School of Public Health, University of Toronto; 2: School of Mathematics, University of Manchester} 
\usepackage{amsmath,subfigure,alltt}
\setkeys{Gin}{width=\columnwidth}

@@

\begin{block}{Histogram}
<<histPost>>=
hist(paramSample[,"probs.D"], breaks=12)
abline(v=params$probs["D"], col="red")
@
\end{block}
\end{columns}
\end{frame}

\begin{frame}[fragile]
\frametitle{Summary Statistics}
<<summaryStats,fig=false>>=
postSummary=t(apply(paramSample, 2, function(qq) 
  c(mean=mean(qq), quantile(qq, prob=c(0.025, 0.5, 0.975)))))
postSummary = cbind(true=unlist(params)[rownames(postSummary)], postSummary)

postSummary[1:12,]
@
\end{frame}

\begin{frame}
\frametitle{Posterior and prior, fatality prob }
<<priorPost, fig=false,results=tex>>=
library(ellipse)
plotPrior(priors, paramSample, transition="HospDeath",file="postFatality", tex=TRUE)
@
\end{frame}

\begin{frame}[fragile]
\frametitle{Hospital demand}
<<hospLoad,echo=T>>=
# generate hospital times
hospSample = simHospitals(paramSample , Ndays=20, NinfectionsPerDay=10)

# graph hospital times
plotHospitals(hospSample)
@
\end{frame}
